Visualizations for the manuscript

### 2022-03-23 metanalysis_visualization/manuscript_Figures.Rmd
forest plot: reordering and changing square sizes proportions

forest(model_meta_country, 
       slab = trends_country$country,
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
```

>>>>

forest(model_meta_country, 
       slab = trends_country$country,
       plim = c(1, NA),
       order = "obs", 
       showweights = TRUE,
       header = "Countries",
       mlab = "Overall periods' slope differences")
```
